Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-01-25 msr/msr2011.tex
edit contributions
previous work edits

This paper makes the following contributions: 
\begin{itemize}
\item We introduce the concept of labelled topic extraction, using a non-functional requirements (NFR) taxonomy for our labels. 
\item We evaluate an unsupervised method of automated topic labelling (word-lists);
%\item Our unsupervised method can be applied to projects without training;
\item We evaluate a supervised method of automatically labelling topics with a single NFR (machine learning);
\item We evaluate a supervised method of labelling topics with multiple NFRs (multi-label machine learning);
\item We provide a method of cross-project analysis via topic labelling;
\item We apply these techniques to visualizing NFRs over time, to analyze maintenance activities.
\end{itemize}

@@

The idea of extracting higher-level `concerns', also known as `concepts', `aspects' or `requirements', has been approached from documentation-based and repository-based perspectives.

@@

% in our previous work~\cite{Hindle09ICSM}, as well as -- CITED a little too often (vanity cites!)
In Baldi et al.~\cite{Baldi2008}, topics are named manually: human experts read the highest-frequency members of a topic and assign a label accordingly. 
As discussed earlier, given the topic \emph{``listener change remove add fire''}, Baldi et al. would assign the label \emph{event-handling}. 
The labels are reasonable enough, but still require an expert in the field to determine them. 
Furthermore, these labels are project-specific, because they are generated from the data of that project. E.g., we might have a label called `Oracle' in the MySQL case, since Oracle owns MySQL.

This paper does this differently. First of all, we automated the process of naming the topics. Secondly, we labelled topics with project-independent terms, in order to permit cross-project comparison.

>>>>

This paper makes the following contributions: 
\begin{itemize}
\item We introduce the concept of labelled topic extraction, using a non-functional requirements (NFR) taxonomy for our labels. 
\item We evaluate an unsupervised method of automated topic labelling (word-lists);
%\item Our unsupervised method can be applied to projects without training;
\item We evaluate a supervised method of automatically labelling topics with a single NFR (machine learning);
\item We evaluate a supervised method of labelling topics with multiple NFRs (multi-label machine learning);
\item We provide a method of cross-project analysis via topic labelling;
\item We apply these techniques to visualize NFRs over time, and to analyze maintenance activities.
\end{itemize}

@@

The idea of extracting higher-level \emph{concerns}, also known as \emph{concepts}, \emph{aspects} or \emph{requirements}, has been approached from documentation-based and repository-based perspectives.

@@

% in our previous work~\cite{Hindle09ICSM}, as well as -- CITED a little too often (vanity cites!)
In Baldi et al.~\cite{Baldi2008}, topics are named manually: human experts read the highest-frequency members of a topic and assign a label accordingly. 
As discussed earlier, given the topic \emph{``listener change remove add fire''}, Baldi et al. would assign the label \emph{event-handling}. 
The labels are reasonable enough, but still require an expert in the field to determine them. 
Furthermore, these labels are project-specific, because they are generated from the data of that project. E.g., we might have a label called `Oracle' in the MySQL case, since Oracle owns MySQL. 
We do this differently.
%This paper does this differently. 
First of all, we automated the process of naming the topics. Secondly, we labelled topics with project-independent terms, in order to permit cross-project comparison.
